\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2020-12-14 popl-2019-journal-v/discussion.tex
Add file with JFP reviews in order to collect responses, fix trivial typos already.

With the technical results established, it's worth taking a step back and discuss our work from a moreo high-level perspective.
In the next sections, we specifically give some more thoughts on our use of full abstraction to express WBCF and LSE, and the practical usability of \stktokens{}.

@@

  % TODO new paragraph: Machine checked proof. MANY details, any future work should be machine checked?
  One challenge in full-abstraction proofs is to construct source language contexts that emulate the behavior of an arbitrary target language context.
  This construction is known as a back-translation  \citep{devriese_modular_2017}, i.e.\ a translation from the target language to the source language.
  When we use an overlay semantics, the back-translation becomes trivial because the source and target language are syntactically the same, so the identity can be used as the back-translation.
  If we have native call and return instructions in the source language, then the source language would be different from the target language, and we would have to use a non-trivial back-translation.
  Specifically, the back-translation would need to distinguish sequences of instructions that is the translation of a call from sequences of instructions that just look like a call.
  With overlay semantics, this is not a concern because everything that looks like a call is interpreted as a call.
\end{jversion}

>>>>

With the technical results established, it's worth taking a step back and discuss our work from a more high-level perspective.
In the next sections, we specifically give some more thoughts on our use of full abstraction to express WBCF and LSE, and the practical usability of \stktokens{}.

@@

  % TODO new paragraph: Machine checked proof. MANY details, any future work should be machine checked?
  One challenge in full-abstraction proofs is to construct source language contexts that emulate the behavior of an arbitrary target language context.
  This construction is known as a back-translation  \citep{devriese_modular_2017}, i.e.\ a translation from the target language to the source language.
  When we use an overlay semantics, the back-translation becomes trivial because the source and target language are syntactically the same, so the identity can be used as the back-translation.
  If we have native call and return instructions in the source language, then the source language would be different from the target language, and we would have to use a non-trivial back-translation.
  Specifically, the back-translation would need to distinguish sequences of instructions that are the translation of a call from sequences of instructions that just look like a call.
  With overlay semantics, this is not a concern because everything that looks like a call is interpreted as a call.
\end{jversion}
